Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-11-13 DryDep_supplement.tex
Started to include the actual resuls into the documents and updated some plots.
A lot about sensitivity studies and some new plots.

\subsection*{S.5 De-accumulation of photosynthetic active radiation (PAR) from OpenIFS: January 2nd 2005}
\subsubsection*{S.5.1 Output from OpenIFS: Accumulated PAR}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.75cm 0.75cm 0.75cm 0.75cm}]{pictures/PAR_as_is.png}
\end{center}
\subsubsection*{S.5.2 Partly de-accumulated}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.75cm 0.75cm 0.75cm 0.75cm}]{pictures/PAR_partly_deaccumulated.png}
\end{center}
\subsubsection*{S.5.3 De-accumulation of hour 00}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.75cm 0.75cm 0.75cm 0.75cm}]{pictures/PAR_deaccumulating_00h.png}
\end{center}

\end{document}

>>>>

\subsection*{S.5 De-accumulation of photosynthetic active radiation (PAR) from OpenIFS: January 2nd 2005}
\subsubsection*{S.5.1 Output from OpenIFS: Accumulated PAR}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.7cm}]{pictures/PAR_as_is.png}
\end{center}
\subsubsection*{S.5.2 Partly de-accumulated}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.7cm}]{pictures/PAR_partly_deaccumulated.png}
\end{center}
\subsubsection*{S.5.3 De-accumulation of hour 00}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.75cm 0.75cm 0.75cm 0.75cm}]{pictures/PAR_deaccumulating_00h.png}
\end{center}

\subsection*{S.6 Average ozone dry deposition velocity seperated by land surface type (southern hemisphere)}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/final-total_ozone_drydepvelo_monthly_pft_sh}
\end{center}
\end{document}
